The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-28 science_ms.tex
Combined the Pop III and II SF sections and shortened the 3rd paragraph of the "mass evolution" section.

The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
driven by ionization fronts and blastwaves in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction because halos with $M < M_f$ are likely photo-evaporated,
hosting diffuse warm gas reservoirs instead of cold dense cores.
After $z=10$, the halo mainly accretes warm diffuse gas from the
filaments and IGM.  In contrast, the intense halo grows from major
mergers of halos with $M > M_f$.  The progenitor halos involved in the
major mergers are able to host molecular clouds and have higher gas
fractions.  Between $z=10$ and $z=8$, the gas fraction increases from
0.07 to 0.12 until it jumps to 0.14 when a gas-rich major merger
occurs.  The stellar mass accordingly increases with the ample supply
of gas during this period.  The gas fraction then decreases by 0.01
when galactic outflows are generated from the starburst associated
with this major merger.

@@

\subsection*{Population III star formation history}

@@

\subsection*{Population II stellar populations}
\label{sec:pop}

>>>>

The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
driven by ionization fronts and blastwaves in their initial
starbursts.  The quiet halo does not have a major merger with any halo
with $M > M_f$, leading to a small final gas fraction.  These low-mass
halos are photo-evaporated, hosting diffuse warm gas reservoirs
instead of cold dense cores.  After $z=10$, the halo mainly accretes
warm diffuse gas from the filaments and IGM.  In contrast, the intense
halo grows from major mergers of halos with $M > M_f$.  The progenitor
halos involved in the major mergers are able to host molecular clouds
and have higher gas fractions.  Between $z=10$ and $z=8$, the gas
fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
gas-rich major merger occurs.  The stellar mass accordingly increases
with the ample supply of gas during this period.

% The gas fraction then decreases by 0.01 when galactic outflows are
% generated from the starburst associated with this major merger.

@@

\subsection*{Star formation history}
\label{sec:pop}

@@

%\subsection*{Population II stellar populations}
%\label{sec:pop}
